Predictive modeling with cross validation

### 2017-08-22 model fitting/cross_validation.Rmd
more work with splines + variable selection

```{r, echo = FALSE}
# write a function to set up variables for this training data

train1 <- x[splitPlan[[1]]$train, ]

@@

@@

# all signficant interaction terms 
model_i <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
AIC(model_i, k = 2) # 65263.35
```

>>>>

```{r, echo = FALSE}
train1 <- x[splitPlan[[1]]$train, ]

@@

### splines/square root transformed variables

```{r, echo = FALSE}
fit3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday, data = train1)

fit4 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + sqrt(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday, data = train1)
model4 <- MASS::stepAIC(fit4, direction = "both", k = 2)

#AIC=64986.23
model3 <- MASS::stepAIC(fit3, direction = "both", k = 2)

resultsa <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday, data = train1)
summary(resultsa)
AIC(resultsa, k = 2) # 64965.19

# adding in spline on device_length
resultsb <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC"), data = train1)
summary(resultsb)
AIC(resultsb, k = 2) # 64908.37

# adding in spline on

results3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + 
    pspline(device_length, df = 0, method = "AIC") + contain_unanswered + 
    title_questionmark + sqrt(avg_tag_score) + contain_answered + 
    text_all_lower + update + num_prior_effort + ampm + weekday + 
    pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
summary(results3)
AIC(results3, k = 2) # 64891.93

results4 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + pspline(device_length, df = 0, method = "AIC") + contain_unanswered + title_questionmark + sqrt(avg_tag_score) + contain_answered + text_all_lower + update + prior_effort + ampm + weekday + sqrt(newline_ratio) + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
summary(results4)

AIC(results4, k = 2) # 64888.83
summary(results4)

```

@@

# all signficant interaction terms 
model_i <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
AIC(model_i, k = 2) # 65263.35
summary(model_i)
```
